\begin{thebibliography}{9}

\bibitem{mit_injector} 
MIT Rocket Team. (2023). \textit{Topic 6: Injector Design}. Retrieved from \url{https://wikis.mit.edu/confluence/display/RocketTeam/Topic+6%3A+Injector+Design}.

\bibitem{halfcat_mojave} 
HalfCat Rocketry. (2023). \textit{Mojave Sphinx Hybrid Rocket Project}. Retrieved from \url{https://www.halfcatrocketry.com/mojave-sphinx}.

\bibitem{questionable_engineer} 
Questionable Engineer. (2023). \textit{Questionable Engineer - Rocket Engine Design and Engineering Channel}. Retrieved from \url{https://www.youtube.com/@QuestionableEngineer}.

\bibitem{huzel1971} 
Huzel, D. K., \& Huang, D. H. (1971). \textit{Modern Engineering for Design of Liquid Propellant Rocket Engines}. Progress in Astronautics and Aeronautics. American Institute of Aeronautics and Astronautics (AIAA).

\bibitem{eos_inconel} 
EOS GmbH - Electro Optical Systems. (2023). \textit{Material Datasheet - EOS Nickel Alloy IN718}. Retrieved from \url{https://vetted3d.com/pdf/materials/material_datasheet_eos_nickelalloy_in718_en.pdf}.

\bibitem{sutton} 
Sutton, G. P., \& Biblarz, O. (2016). \textit{Rocket Propulsion Elements} (9th ed.). Wiley.

\bibitem{waxman2014} 
Waxman, B. S. (2014). \textit{An Investigation of Injectors for Use with High Vapor Pressure Propellants with Applications to Hybrid Rockets} (Ph.D. dissertation). Stanford University. Retrieved from \url{https://purl.stanford.edu/ng346xh6244}.


\bibitem{martinez2020}
Martínez\-Maradiaga, D., Mishin, O. V., \& Engelbrecht, K. (2020). Thermal properties of selectively laser-melted AlSi10Mg products with different densities. \textit{Journal of Materials Engineering and Performance, 29}(11), 7125–7130. \url{https://doi.org/10.1007/s11665-020-05192-z}.
\end{thebibliography}